Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-27 ms.tex
more

\subsection{Stellar winds} 
{\bf AG: This section may have to be substantially modified in light
  of our more careful analysis of stellar winds.}

Although most of the mass supplied to the CNM by stellar winds occurs
during the giant AGB phase, these winds represent a negligible heating
source compared to the random wind velocity because the wind velocity
$\lesssim 40$ km s$^{-1}$ is much less than the stellar potential
$\sigma$.

Main sequence winds, though contributing a much smaller quantity of
mass, have much higher velocities and hence contribute a
disproportionally large share of the kinetic energy of winds.
\citet{NaimanSoares-Furtado+:2013a} estimate that $v_{w} \sim
100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old
stellar population.  On the other hand, for a very young stellar
population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind
heating from massive stars can be much greater, $\gtrsim 10^{3}$ km
s$^{-1}$.  In Appendix \ref{app:windheat} we present a model for
how $v_{w}$ varies as a function of stellar age.

>>>>

\subsection{Stellar winds}

Energy and mass input to the CNM by stellar winds is the sum of contributions from main sequence and post-main sequence stars.  At early times following star formation, energy input is dominated by core collapse supernovae and by the fast outflows of Wolf-Rayet stars, while at later times energy input is dominated by main sequence winds.  Mass input is also dominated by massive stars for very young stellar populations, but for most stellar ages mass input is dominated by the slow AGB winds of low mass stars.

Appendix \ref{app:windheat} provides a calculation of wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age $\tau_{\star}$ of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).  At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating is much lower, $v_{\rm w} \sim 50 $ km s$^{-1}$ (see also \citealt{NaimanSoares-Furtado+:2013a}).  As we describe in $\S$, the net heating rate produced by stellar winds in the case of quasi-continuous star formation, as representative of the average star formation history of low mass galaxies, can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.  Thus stellar winds contribute a potentialy important source of energy as well as mass for the CNM.

### 2015-01-27 windheat.tex
Incorporating impulsive eta figure into appendix
more

The effective wind velocity in the limit of an impulsive star formation may then be written
as 
\begin{align}
\bar{v}_w(t)=2 \dot{\bar{e}}(t)/\dot{\bar{m}}(t)
\label{eq:vwImp}
\end{align}
while {\bf BDM: insert correct expression}
\begin{align}
\eta = \dot{\bar{m}}(t)
\label{eq:vwImp}
\end{align}
We plot $\bar{v}_w(t)$ and $\eta(t)$ in Figures~\ref{fig:vwImp} and XXX.

\begin{figure}
\includegraphics[width=\columnwidth]{vwImp.pdf}
\caption{\label{fig:vwImp} The effective $\vw$ from stellar winds from
  a stellar population of age $t$.}
\end{figure}

>>>>

The effective wind velocity in the limit of an impulsive star formation may then be written
as 
\begin{align}
\bar{v}_w(t)=2 \dot{\bar{e}}(t)/\dot{\bar{m}}(t)
\label{eq:vwImp}
\end{align}
while {\bf BDM: insert correct expression}
\begin{align}
\eta = \dot{\bar{m}}(t)
\label{eq:vwImp}
\end{align}
We plot $\bar{v}_w(t)$ and $\eta(t)$ in Figures~\ref{fig:vwImp} and~\ref{fig:etaImp}.

\begin{figure}
\includegraphics[width=\columnwidth]{vwImp.pdf}
\caption{\label{fig:vwImp} The effective heating rate, $\vw^{\star}$, from stellar winds from
  a stellar population of age $\tau_{\star}$.  {\bf BDM: change axis label to $\tau_{\star}$}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{etaImp.pdf}
\caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
  a stellar population of age $\tau_{\star}$.  {\bf BDM: change axis label to $\tau_{\star}$}}
\end{figure}
